Open source landscape ecology tools \thanks{Grants or other notes about the article that should go on the front page should be placed here. General acknowledgments should be placed at the end of the article.}

### 2020-06-08 Outline.Rmd
Use paper-folder for manuscript

### Open questions:
- Remote sensing/GIS?
- Landscape genetics?
- Landscape Connectivity?
- Some "results"/meta-analysis of increase of R in landscape ecology?
- Missing packages
    - surface metrics
    - vector-based metrics
- ...

>>>>

### Open questions:
- Remote sensing/GIS?
- Landscape genetics?
- Landscape Connectivity?
  - ResistanceGA
  - LQGraph
- Some "results"/meta-analysis of increase of R in landscape ecology?
- Open-source licenses
- Missing packages
    - surface metrics
    - vector-based metrics
- ...

### 2020-06-08 paper/paper.Rmd
Use paper-folder for manuscript

---
title: Open source landscape ecology tools
subtitle: Do you have a subtitle? If so, write it here
titlerunning: Open source landscape ecology tools
authorrunning: Short form of author list if too long for running head
thanks: | 
    Grants or other notes about the article that should go on the front 
    page should be placed here. General acknowledgments should be placed at the
    end of the article.

authors: 
- name: Maximillian H.K. Hesselbarth
  address: Department of Ecosystem Modelling, University of Goettingen, Buesgenweg 4, 37077 Goettingen, Germany
  email: maximilian.hesselbarth@uni-goettingen.de

- name: Jakub Nowosad
  address: Institute of Geoecology and Geoinformation, Adam Mickiewicz University, Krygowskiego 10, 61-680 Poznan, Poland
  email: nowosad.jakub@gmail.com

keywords:
- key
- dictionary
- word

abstract: |
  The text of your abstract.  150 -- 250 words.

@@

Your text comes here. Separate text sections with \cite{Mislevy06Cog}.

@@

Text with citations by \cite{Galyardt14mmm}.

>>>>

---
title: Open source landscape ecology tools
# subtitle: Do you have a subtitle? If so, write it here
# titlerunning: Open source landscape ecology tools
# authorrunning: Short form of author list if too long for running head

thanks: | 
    Grants or other notes about the article that should go on the front 
    page should be placed here. General acknowledgments should be placed at the
    end of the article.

authors: 
- name: Maximillian H.K. Hesselbarth
  address: Department of Ecosystem Modelling, University of Goettingen, Buesgenweg 4, 37077 Goettingen, Germany
  email: maximilian.hesselbarth@uni-goettingen.de
- name: Jakub Nowosad
  address: Institute of Geoecology and Geoinformation, Adam Mickiewicz University, Krygowskiego 10, 61-680 Poznan, Poland
  email: nowosad.jakub@gmail.com
- name: Author 3
  address: Adress author 3
  email: E-Mail author 3
- name: ...
  address: ...
  email: ...

keywords:
- keyword 1
- keyword 2
- keyword 3
- keyword 4
- ...

abstract: |
  max. (200 words) Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract

@@

Landscape ecology does this and that \cite{turner2005}.

@@

Open-source is great \cite{sandve2013}.

### 2020-06-08 paper/paper.tex
Use paper-folder for manuscript

\title{Open source landscape ecology tools \thanks{Grants or other notes about the article that should go on the front page
should be placed here. General acknowledgments should be placed at the
end of the article.} }
 \subtitle{Do you have a subtitle? If so, write it here}

    \titlerunning{Open source landscape ecology tools}

\author{  Maximillian H.K. Hesselbarth \and  Jakub Nowosad \and  }

    \authorrunning{ Short form of author list if too long for running head }

\institute{
        Maximillian H.K. Hesselbarth \at
     Department of Ecosystem Modelling, University of Goettingen, Buesgenweg
 4, 37077 Goettingen, Germany \\
     \email{\href{mailto:maximilian.hesselbarth@uni-goettingen.de}{\nolinkurl{maximilian.hesselbarth@uni-goettingen.de}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Jakub Nowosad \at
     Institute of Geoecology and Geoinformation, Adam Mickiewicz University,
 Krygowskiego 10, 61-680 Poznan, Poland \\
     \email{\href{mailto:nowosad.jakub@gmail.com}{\nolinkurl{nowosad.jakub@gmail.com}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
    }

@@

\begin{abstract}
The text of your abstract. 150 -- 250 words.
\\
\keywords{
        key \and
        dictionary \and
        word \and
    }

>>>>

\title{Open source landscape ecology tools \thanks{Grants or other notes
about the article that should go on the front page should be placed
here. General acknowledgments should be placed at the end of the
article.} }

\author{  Maximillian H.K. Hesselbarth \and  Jakub Nowosad \and  Author
3 \and  \ldots{} \and  }

\institute{
        Maximillian H.K. Hesselbarth \at
     Department of Ecosystem Modelling, University of Goettingen,
Buesgenweg 4, 37077 Goettingen, Germany \\
     \email{\href{mailto:maximilian.hesselbarth@uni-goettingen.de}{\nolinkurl{maximilian.hesselbarth@uni-goettingen.de}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Jakub Nowosad \at
     Institute of Geoecology and Geoinformation, Adam Mickiewicz
University, Krygowskiego 10, 61-680 Poznan, Poland \\
     \email{\href{mailto:nowosad.jakub@gmail.com}{\nolinkurl{nowosad.jakub@gmail.com}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Author 3 \at
     Adress author 3 \\
     \email{E-Mail author 3}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        \ldots{} \at
     \ldots{} \\
     \email{\ldots{}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
    }

@@

\begin{abstract}
max. (200 words) Abstract Abstract Abstract Abstract Abstract Abstract
Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract
Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract
Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract
Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract
Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract
Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract
Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract
Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract
Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract
Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract
Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract
Abstract Abstract Abstract Abstract Abstract Abstract
\\
\keywords{
        keyword 1 \and
        keyword 2 \and
        keyword 3 \and
        keyword 4 \and
        \ldots{} \and
    }
